---
title: "HW2"
output: github_document
---
```{r setup}
library(tidyverse)
```


```{r}
Trash_data = 
  readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "Mr. Trash Wheel",
    range = "A2:N533" ,
    na  = "")  %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(sports_balls = round(sports_balls))
```

```{r}
precipitation_2019_data = 
    readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "2019 Precipitation",
    range = "A2:B14") %>%
    mutate(year = "2019")

precipitation_2018_data =
     readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "2018 Precipitation",
    range = "A2:B14") %>%
    mutate(year = "2018")
precipitation_df =  bind_rows(precipitation_2019_data,precipitation_2018_data) %>%
  janitor::clean_names() %>%
  mutate(month = month.name[month])

```
 

There is `nrow(Trash_data)` in Mr. Trash Wheel data set and there is `nrow(precipitation_df)` in the combination of precipitation in 2018 and in 2019. There are `names(Trash_data)` in Mr. Trash Wheel data set and there are `names(precipitation_df)`.The total precipitation in 2018 `r sum(pull(filter(precipitation_df,year == 2018),total))`.The median number of sports balls in a dumpster in 2019 `r median(pull(filter(Trash_data, year == 2019),sports_balls))`.








    







 


