---
title: "HW2"
output: github_document
---

##Problem 1
```{r setup}
library(tidyverse)
library(dplyr)
```

#Read and clean the Mr. Trash Wheel sheet:
```{r}
Trash_data = 
  readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "Mr. Trash Wheel",
    range = "A2:N533" ,
    na  = "")  %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(sports_balls = round(sports_balls))
```
#Read and clean precipitation data for 2018 and 2019. 
```{r}
precipitation_2019_data = 
    readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "2019 Precipitation",
    range = "A2:B14") %>%
    mutate(year = "2019")

precipitation_2018_data =
     readxl::read_excel(
    "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
    sheet = "2018 Precipitation",
    range = "A2:B14") %>%
    mutate(year = "2018")
precipitation_df =  bind_rows(precipitation_2019_data,precipitation_2018_data) %>%
  janitor::clean_names() %>%
  mutate(month = month.name[month])

```
 
In Mr. Trash Wheel data set, it has `r nrow(Trash_data)` and contains `r names(Trash_data)` variables. In the combination of precipitation, it has `r nrow(precipitation_df)`observations and the variables are `r names(precipitation_df)` in the precipitation. 
The total precipitation in 2018 is `r sum(pull(filter(precipitation_df,year == 2018),total))`.
The median number of sports balls in a dumpster in 2019 is `r median(pull(filter(Trash_data, year == 2019),sports_balls))`.


##Problem 2
#clean the data in pols-month.csv.
```{r}
pols_df = read_csv("./data/fivethirtyeight_datasets/pols-month.csv") %>%
   janitor::clean_names() %>%
   separate(mon, into = c("year","month","day")) %>%
   mutate(year = as.integer(year),
          month = as.integer(month),
          day = as.integer(day)) %>%
   mutate(month = month.name[month]) %>%
   mutate(president = ifelse(prez_dem == "1","dem","gop")) %>%
   select(-prez_dem,-prez_gop,-day)
```
#clean the data in snp.csv
```{r}
snp_df = read_csv("./data/fivethirtyeight_datasets/snp.csv") %>%
   janitor::clean_names() %>%   
   mutate(date = lubridate::mdy(date)) %>%
   separate(date, into = c("year","month","day")) %>%
   mutate(year = as.integer(year),
          month = as.integer(month),
          day = as.integer(day)) %>%
   mutate(month = month.name[month]) %>%
   select(-day)
```
#tidy the unemployment data
```{r}
unemployment_data = read_csv("./data/fivethirtyeight_datasets/unemployment.csv") %>%
    janitor::clean_names() %>%
 pivot_longer(
    jan:dec,
    names_to = "month",
    values_to = "rate"
  )
```



# Join the datasets
```{r}
pols_snp = left_join(pols_df,snp_df, by = c("year","month"))
```

pols-month contains `r nrow(pols_df)` and has variable including `r names(pols_df)`. It range between `r min(range(pull(pols_df,year)))` and `r max(range(pull(pols_df,year)))`.

snp contains `r nrow(snp_df)` and has variable including `r names(snp_df)`. It range between 
`r min(range(pull(snp_df,year)))` and `r max(range(pull(snp_df,year)))`.
unemployment contains `r nrow(unemployment_data)` and has variable including `r names(unemployment_data)`.It range between `r min(range(pull(unemployment_data,year)))` and `r max(range(pull(unemployment_data,year)))`.

##Problem 3

#Load and tidy the data. Produce a well-structured, reader-friendly table for female whose name is Olivia.
```{r,message=FALSE}
Baby_df = 
   read_csv("./data/Popular_Baby_Names.csv") %>%
   janitor::clean_names() %>%   
   mutate(ethnicity = recode(ethnicity, "ASIAN AND PACI" = "ASIAN AND PACIFIC ISLANDER","WHITE NON HISP" = "WHITE NON HISPANIC", "BLACK NON HISP" = "BLACK NON HISPANIC")) %>%
   mutate(childs_first_name = toupper(childs_first_name)) %>%
   distinct(childs_first_name,year_of_birth,gender,ethnicity,.keep_all = TRUE) %>%
   filter(childs_first_name == "OLIVIA", gender == "FEMALE") 
Baby_df %>%
  janitor::clean_names() %>%
  arrange(year_of_birth) %>%
  pivot_wider(
    names_from = "year_of_birth",
    values_from = "rank"
  ) %>%
  select(-count) %>%
  relocate(childs_first_name,gender,ethnicity)
```
In this problem, I use `unique(pull(Baby_df,childs_first_name))` and ` unique(pull(Baby_df,ethnicity))` to check the change of string variable over time.


#Produce a well-structured, reader-friendly table for male whose name is the most popular
```{r,message=FALSE}
Baby_male_df = 
  read_csv("./data/Popular_Baby_Names.csv") %>%
   janitor::clean_names() %>%   
   mutate(ethnicity = recode(ethnicity, "ASIAN AND PACI" = "ASIAN AND PACIFIC ISLANDER","WHITE NON HISP" = "WHITE NON HISPANIC", "BLACK NON HISP" = "BLACK NON HISPANIC")) %>%
   mutate(childs_first_name = toupper(childs_first_name)) %>%
   distinct(childs_first_name,year_of_birth,gender,ethnicity,.keep_all = TRUE) %>%
   filter(gender == "MALE",rank == 1) %>%
   pivot_wider(
    names_from = "year_of_birth",
    values_from = "rank"
    ) %>%
   janitor::clean_names() %>%
   relocate(gender,childs_first_name)
```
#Create a scatter plot for male, white non-hispanic children born in 2016
```{r,message=FALSE}
children_2016 = 
   read_csv("./data/Popular_Baby_Names.csv") %>%
   janitor::clean_names() %>% 
   mutate(ethnicity = recode(ethnicity, "ASIAN AND PACI" = "ASIAN AND PACIFIC ISLANDER","WHITE NON HISP" = "WHITE NON HISPANIC", "BLACK NON HISP" = "BLACK NON HISPANIC")) %>%
   distinct(childs_first_name,year_of_birth,gender,ethnicity,.keep_all = TRUE) %>%
   filter(gender == "MALE",ethnicity == "WHITE NON HISPANIC", year_of_birth == 2016) %>%
   ggplot(aes(rank, count)) + geom_point()

```









 


